\documentclass[11pt]{article}

\usepackage{amsmath}
\usepackage{textcomp}
\usepackage[top=0.8in, bottom=0.8in, left=0.8in, right=0.8in]{geometry}
% add other packages here

% put your group number and names in the author field
\title{\bf Exercise 2: A Reactive Agent for the Pickup and Delivery Problem}
\author{Group \textnumero: 272257, 262609}

% the report should not be longer than 3 pages

\begin{document}
\maketitle

\section{Problem Representation}

\subsection{Representation Description}
% describe how you design the state representation, the possible actions, the reward table and the probability transition table

 	The problem studied in this report is the classical pickup and delivery problem. We try here specifically to implement one agent (which will be reffered to as \emph{the truck} or the agent interchangibly from now on). Here we try to implement the truck as a reactive agent. 
 	To properly explain the comportment of the agent, we need to clearly state what are : \emph{the states}, \emph{the actions}, \emph{the reward table}, and \emph{the probability transition table}.
 	\begin{itemize}
 		 \item[$\bullet$] States: The state is supposed to represent the perception the agent has of the environnement. Once the agent finishes an action (see definition of actions), it observes two things: the city it arrived at and the contract given from the given city. We then design the states as having two attributes: the city the agent is currently in and the contract present. Note that \bold{the absence of contract is modelized by a contract from the current city to itself}.
 		 
 		 \item[$\bullet$] Actions: An action is designed as the movement from a city to another. Note that actions can move the agent from any city to any other one \bold{even if the two cities are not connected directly}.
 		 
 		 \item[$\bullet$] Reward table: The reward table is $\# States\times\# Actions$ table in which each cell contains the expected value of 
 		 
\subsection{Implementation Details}.
% describe the implementation details of the representations above and the implementation details of the reinforcement learning algorithm you implemented

%Action
In this impletation, we implement the actions as the class \emph{ActionMDP}, which comprises of two variables: one being \emph{City startState}, that represents the city the truck is currently in, andthe other \emph{City endState}, that represents the city will be in if the truck chooses the given action. Note that an action can take the agent from one node to another \bold{even if those two nodes are not connected}. 

%State 
 In this fashion, we implement the state as a class comprising of two variables: one called \emph{city} which represents the city the truck is currently will, and one called \emph{action} which represents the action available to the truck when and if the truck arrives to that city.
 
 %Reward table
 We then get that 
 			\begin{align*}
 				rewardFunction(s,a)= 
 					\begin{cases}
 						0 & \mathrm{if}\ a.startState\neq state.city,\\
 						r(s.city,a) & \mathrm{otherwise}
					\end{cases}
			\end{align*}
where $r(s.city,a)$ is the entry in the reward table corresponding to the a given state $s$ and a given action $a$.
 
 %Transition table

\section{Results}
% in this section, you describe several results from the experiments with your reactive agent

\subsection{Experiment 1: Discount factor}
% the purpose of this experiment is to understand how the discount factor influences the result

\subsubsection{Setting}
% you describe how you perform the experiment (you also need to specify the configuration used for the experiment)

\subsubsection{Observations}
% you describe the experimental results and the conclusions you inferred from these results

\subsection{Experiment 2: Comparisons with dummy agents}
% you compare the results of your agent with two dummy agents: the random agent that was already given in the starter files and another dummy agent that you define and create. You should report the results from the simulations using the topologies given in the starter files and optionally, additional topologies that you create.

\subsubsection{Setting}
% you describe how you perform the experiment and you describe the dummy agent you created (you also need to specify the configuration used for the experiment)

\subsubsection{Observations}
% elaborate on the observed results

\vdots

\subsection{Experiment n}
% other experiments you would like to present

\subsubsection{Setting}

\subsubsection{Observations}

\end{document}